---
title: "Organizing and harmonizing RBC data"
author: "Megan Jones"
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Study-level information

We are planning to use the phenotype: age, internalizing_mcelroy_harmonized_all_samples, externalizing_mcelroy_harmonized_all_samples
We will also adjust models for: Euler number, Mean frame displacement (FD)

```{r}
library(readr)
library(dplyr)
library(magrittr)
library(purrr)

# list the five studies
studies = c("BHRC", "CCNP", "HBN", "NKI", "PNC")

RBC_path = "/media/disk2/RBC_version0.1/"

# get the demographic, structural QC, and functional QC for each study
for (s in studies){
  assign(paste0("demo_",s), read_tsv(paste0(RBC_path, s, "_BIDS/study-", s, "_desc-participants.tsv")))
  assign(paste0("func_qc_",s), read_tsv(paste0(RBC_path, s, "_CPAC/cpac_RBCv0/study-", s, "_desc-functional_qc.tsv")))
  assign(paste0("t1_qc_",s), read_tsv(paste0(RBC_path, s, "_FreeSurfer/study-", s, "_desc-T1_qc.tsv")))
}
```

# Individual Files

## Structural

Extract the regional GMV for each participant, from both the Desikan-Killiany-Tourville atlas, and the Schaefer 300 (17 Network) atlas 

```{r}
for (s in studies){
  # Define the directory containing the subject folders
  base_dir <- paste0(RBC_path, s, "_FreeSurfer/freesurfer")
  
  # may need to do the pattern per study (Session info differs)
  # Find all the FC files recursively
  assign(paste0("struct_files_",s), list.files(
    path = base_dir,
    pattern = "_regionsurfacestats.tsv$",
    full.names = TRUE,
    recursive = TRUE
  ))
  
 
  # Read and combine all files, tagging each with subject ID
  # FC_BHRC <- map_dfr(tsv_files, function(file) {
  #   # Extract subject ID from filename
  #   #subject_id <- sub(".*sub-([0-9]+)_ses-2.*", "sub-\\1", file)
  #   
  #   read_tsv(file, show_col_types = FALSE)
  # })
}

struct_files_BHRC = grep("_ses-1", struct_files_BHRC, value = TRUE)
struct_files_NKI = grep("-BAS1", struct_files_NKI, value = TRUE)
```

```{r, eval=FALSE}
# checking data is present for all participants
for (s in studies){
  # List all subfolders matching the pattern
  subject_dirs = list.dirs(paste0(RBC_path,s,"_FreeSurfer/freesurfer/"), recursive = F, full.names = FALSE)
  
  if(s == "BHRC"){
    subject_dirs = grep("_ses-1", subject_dirs, value = TRUE)
  }
  
  if(s == "NKI"){
    subject_dirs = grep("_ses-BAS1$", subject_dirs, value = TRUE)
  }

  assign(paste0("all_struct_ids_", s), gsub(".*(sub-[^_/]+).*", "\\1", subject_dirs))
  assign(paste0("downloaded_struct_ids_", s), gsub(".*(sub-[^_/]+).*", "\\1", get(paste0("struct_files_", s))))
}

# got all downloaded structural data
```

```{r}
# add all structural data to one dataset
temporalpole_ids = frontalpole_ids = c()
for (s in studies){
  demo = get(paste0("demo_", s))
  t1_qc = get(paste0("t1_qc_", s))
  dataset_struct = data.frame()
  for(f in get(paste0("struct_files_", s))){
    # individual id
    # also keep DKT atlas (62) in case of future need for lower dim
    struct <- read_tsv(f, show_col_types = F)
    id = sub("sub-", "", struct$subject_id[1])
    if("temporalpole" %in% unlist(struct[struct$atlas == "aparc.DKTatlas", "StructName"])){
      temporalpole_ids = c(temporalpole_ids, paste0(s,"_",id)) # only some have them
    }
    if("frontalpole" %in% unlist(struct[struct$atlas == "aparc.DKTatlas", "StructName"])){
      frontalpole_ids = c(frontalpole_ids, paste0(s,"_",id)) # only some have them
    }
    struct %<>% filter(atlas %in% c("Schaefer2018_300Parcels_17Networks_order", "aparc.DKTatlas") & !(StructName %in% c("Background+FreeSurfer_Defined_Medial_Wall", "temporalpole", "frontalpole")))
    
    # for DKT, need to add hemisphere to the structname so it is unique
    struct$StructName = ifelse(struct$atlas == "aparc.DKTatlas", paste0(struct$hemisphere, "_", struct$StructName), struct$StructName)

    struct = struct %>% select(StructName, GrayVol) %>% pivot_wider(names_from = StructName, values_from = GrayVol)
    
    # HBN doesn't need session id, NKI is BAS1, PNC is PNC1
    
    demo_sub = demo %>% filter(participant_id == id, session_id %in% c(1, "BAS1", "PNC1", unique(demo_HBN$session_id)))
    
    t1_qc_sub = t1_qc  %>% filter(participant_id == id, session_id %in% c(1, "BAS1", "PNC-1", unique(demo_HBN$session_id))) %>% select(-c(participant_id, session_id, study))
    # concatenate data for one subject
    sub_data_struct = cbind(demo_sub, t1_qc_sub, struct)
    dataset_struct = rbind(dataset_struct, sub_data_struct)
  }
  assign(paste0("struct_", s), dataset_struct)
  }


# combine the five datasets into one
struct_all = rbind(struct_BHRC, struct_CCNP, struct_HBN, struct_NKI, struct_PNC)

# save (unharmonized) version
write.csv(struct_all, paste0(RBC_path, "regional_GMV_all_sites_unharmonized.csv"))
```

## Functional

One file per participant with a 300x300 matrix of regional functional connectivity from the Schaefer 300 atlas. Also need to generate network functional connectivity across the 17 networks

```{r}
# for each study
for (s in studies){
  # Define the directory containing the subject folders
  base_dir <- paste0("/media/disk2/RBC_version0.1/", s, "_CPAC/cpac_RBCv0")
  
  FC_pattern = ".*_task-rest.*atlas-Schaefer2018p300n17_.*36Parameter_desc-PearsonNilearn_correlations.tsv$"
  
  # Find all the FC files recursively
  assign(paste0("FC_files_",s), list.files(
    path = base_dir,
    pattern = FC_pattern,
    full.names = TRUE,
    recursive = TRUE
  ))
}

# need to find the actually downloaded files for HBN
downloaded_FC_files_HBN <- FC_files_HBN[file.exists(FC_files_HBN)]

downloaded_FC_files_NKI = FC_files_NKI[file.exists(FC_files_NKI)]
downloaded_FC_files_PNC = FC_files_PNC[file.exists(FC_files_PNC)]

```

```{r}
# checking data is present for all participants
for (s in studies){
  # List all subfolders matching the pattern
  subject_dirs = list.dirs(paste0(RBC_path,s,"_CPAC/cpac_RBCv0/"), recursive = F, full.names = FALSE)

  assign(paste0("all_FC_ids_", s), gsub(".*(sub-[^_/]+).*", "\\1", subject_dirs))
  assign(paste0("downloaded_FC_ids_", s), gsub(".*(sub-[^_/]+).*", "\\1", get(paste0("downloaded_FC_files_", s))))
}


# make sure these are only appearing because they have a second session or only a anat folder for first session
extra_BHRC = all_FC_ids_BHRC[which(!(all_FC_ids_BHRC %in% downloaded_FC_ids_BHRC))]
missing_BHRC <- extra_BHRC[sapply(extra_BHRC, function(subj) {
  file.exists(file.path(RBC_path, "BHRC_CPAC/cpac_RBCv0", subj, "ses-1/func"))
})]
# some of these had to use run 2 or 3 for QC
# manually add these
BHRC_FC_path = paste0(RBC_path, "BHRC_CPAC/cpac_RBCv0")

missing_BHRC_info <- data.frame(
  id = c("10644", "10788", "10921", "20082", "20141", "20204", "20671", "20880", "20982", "21106"),
  run = c("3", "2", "3", "2", "2", "2", "2", "2", "1", "2"),
  acq = c("", "acq-VARIANTEffectiveEchoSpacing_", "", "", "", "", "", "", "acq-VARIANTNumVolumes_", "")
)

FC_files_BHRC <- c(FC_files_BHRC, sprintf(
  "%s/sub-%s/ses-1/func/sub-%s_ses-1_task-rest_run-%s_%satlas-Schaefer2018p300n17_space-MNI152NLin6ASym_reg-36Parameter_desc-PearsonNilearn_correlations.tsv",
  BHRC_FC_path, missing_BHRC_info$id, missing_BHRC_info$id, missing_BHRC_info$run, missing_BHRC_info$acq
))
 
extra_CCNP = all_FC_ids_CCNP[which(!(all_FC_ids_CCNP %in% downloaded_FC_ids_CCNP))]
get_preferred_CCNP_files <- function(subject_dirs, dataset_root = "/media/disk2/RBC_version0.1/CCNP_CPAC") {
  setwd(dataset_root)

  # List all tracked files
  all_files <- system("git ls-files", intern = TRUE)

  matched_files <- sapply(subject_dirs, function(subj) {
    pattern <- paste0(
      "cpac_RBCv0/", subj,
      "/ses-1/func/",
      subj, "_ses-1_task-rest_run-[0-9]{2}(_[^_]+)?_atlas-Schaefer2018p300n17_.*PearsonNilearn_correlations.tsv$"
    )

    matches <- grep(pattern, all_files, value = TRUE)

    # If multiple runs exist, pick the one with the lowest run number
    if (length(matches) > 0) {
      run_nums <- as.integer(sub(".*_run-([0-9]{2}).*", "\\1", matches))
      matches[which.min(run_nums)]
    } else {
      NA
    }
  })

  matched_files <- na.omit(matched_files)
  return(matched_files)
}

CCNP_files_to_get <- get_preferred_CCNP_files(extra_CCNP)
# get them with datalad
for (f in CCNP_files_to_get) {
  message("Getting ", f)
  system2("datalad", c("get", f))
}



extra_HBN = all_FC_ids_HBN[which(!(all_FC_ids_HBN %in% downloaded_FC_ids_HBN))]
get_preferred_HBN_files <- function(subject_dirs, dataset_root = "/media/disk2/RBC_version0.1/HBN_CPAC") {
  setwd(dataset_root)

  # List all tracked files
  all_files <- system("git ls-files", intern = TRUE)

  matched_files <- sapply(subject_dirs, function(subj) {
    # Regex pattern for that subject, flexible session name and optional VARIANT
    pattern <- paste0(
      "cpac_RBCv0/", subj, "/ses-[^/]+/func/",
      subj, ".*_task-rest_.*_atlas-Schaefer2018p300n17_.*36Parameter_desc-PearsonNilearn_correlations.tsv$"
    ) # make as general as possible

    matches <- grep(pattern, all_files, value = TRUE)

    if (length(matches) > 0) {
      # Pick run with lowest number
      run_nums <- as.integer(sub(".*_run-([0-9]+).*", "\\1", matches))
      matches[which.min(run_nums)]
    } else {
      NA
    }
  })

  matched_files <- na.omit(matched_files)
  return(matched_files)
}
HBN_files_to_get = get_preferred_HBN_files(extra_HBN)
saveRDS(HBN_files_to_get, "/media/disk2/RBC_version0.1/HBN_files_to_get.rds") # get in screen
# still missing many
extra_HBN = all_FC_ids_HBN[which(!(all_FC_ids_HBN %in% downloaded_FC_ids_HBN))] # 595
get_preferred_files_fast <- function(subject_dirs, dataset_root = "/media/disk2/RBC_version0.1/HBN_CPAC") {
  setwd(dataset_root)

  # Get all files once
  all_files <- system("git ls-files", intern = TRUE)

  # Pre-filter to relevant correlation files
  filtered_files <- grep(
    ".*_task-rest.*Schaefer2018p300n17.*36Parameter_desc-PearsonNilearn_correlations.tsv$", 
    all_files, 
    value = TRUE
  )

  # Keep only files within the cpac_RBCv0 pipeline
  filtered_files <- grep("cpac_RBCv0/sub-", filtered_files, value = TRUE)

  # Main loop with progress bar
  best_file <- pbapply::pbsapply(subject_dirs, function(subj) {
    subj_files <- filtered_files[grepl(paste0("cpac_RBCv0/", subj, "/"), filtered_files)]

    if (length(subj_files) == 0) return(NA)

    # Try to extract run number
    run_matches <- regmatches(subj_files, regexpr("_run-\\d+", subj_files))
    run_nums <- as.integer(gsub("_run-", "", run_matches))
    
    if (all(is.na(run_nums))) {
      # No run numbers present — return the first match arbitrarily
      return(subj_files[1])
    } else {
      # Return the file with the lowest run number
      return(subj_files[which.min(run_nums)])
    }
  }, USE.NAMES = TRUE)

  return(na.omit(best_file))
}
HBN_files_to_get = get_preferred_HBN_files_fast(extra_HBN)
HBN_ids_to_get = gsub(".*(sub-[^_/]+).*", "\\1", HBN_files_to_get)
extra_HBN_still = all_FC_ids_HBN[which(!(all_FC_ids_HBN %in% c(downloaded_FC_ids_HBN, HBN_ids_to_get)))]
# some have no func passing qc
check_for_func_HBN = function(subj){
  #browser()
  sess_dirs <- list.dirs(file.path(RBC_path, "HBN_CPAC/cpac_RBCv0", subj), recursive = FALSE, full.names = TRUE)
  
  # Find session directories (e.g., those starting with "ses-")
  sess_dirs <- sess_dirs[grepl("ses-", basename(sess_dirs))]
  
  # Check if any of them has a "func" subfolder
  has_func <- any(file.exists(file.path(sess_dirs, "func")))
}
extra_HBN_still = extra_HBN_still[sapply(extra_HBN_still, check_for_func_HBN)]
# some only have other tasks
has_rest_func <- function(subj, base_dir = "/media/disk2/RBC_version0.1/", site_prefix = "HBN_CPAC/cpac_RBCv0") {
  #browser()
  
  subjects_with_rest <- c()
  
  pb <- progress_bar$new(
    format = "  checking [:bar] :percent eta: :eta",
    total = length(subj),
    clear = FALSE, width = 60
  )
  

    pb$tick()
    
    subj_dir <- file.path(base_dir, site_prefix, subj)
    
    if (!dir.exists(subj_dir)) next
    
    sess_dirs <- list.dirs(subj_dir, recursive = FALSE, full.names = TRUE)
    sess_dirs <- sess_dirs[grepl("ses-", basename(sess_dirs))]
    
    for (sess in sess_dirs) {
      func_dir <- file.path(sess, "func")
      if (!dir.exists(func_dir)) next
      
      files <- list.files(func_dir, pattern = "task-rest", full.names = TRUE, recursive = TRUE)
      return(any(file.exists(files))) 
      
    }

}
extra_HBN_still = extra_HBN_still[sapply(extra_HBN_still, has_rest_func)] # all should be done now
saveRDS(HBN_files_to_get, "/media/disk2/RBC_version0.1/HBN_files_to_get.rds")

```


```{r}
# NKI
extra_NKI = all_FC_ids_NKI[which(!(all_FC_ids_NKI %in% downloaded_FC_ids_NKI))]
NKI_files_to_get = get_preferred_files_fast(extra_NKI, dataset_root = "/media/disk2/RBC_version0.1/NKI_CPAC")
NKI_ids_to_get = gsub(".*(sub-[^_/]+).*", "\\1", NKI_files_to_get)
extra_NKI_still = extra_NKI[!(extra_NKI %in% NKI_ids_to_get)]
saveRDS(NKI_files_to_get, "/media/disk2/RBC_version0.1/NKI_files_to_get.rds")
```

```{r}
extra_PNC = all_FC_ids_PNC[which(!(all_FC_ids_PNC %in% downloaded_FC_ids_PNC))]
PNC_files_to_get = get_preferred_files_fast(extra_PNC, dataset_root = "/media/disk2/RBC_version0.1/PNC_CPAC")
PNC_ids_to_get = gsub(".*(sub-[^_/]+).*", "\\1", PNC_files_to_get)
extra_PNC_still = extra_PNC[!(extra_PNC %in% PNC_ids_to_get)]
saveRDS(PNC_files_to_get, "/media/disk2/RBC_version0.1/PNC_files_to_get.rds")

# ultimately check subject count against qc file if possible
```

```{r}

CCNP_ids_to_get = gsub(".*(sub-[^_/]+).*", "\\1", CCNP_files_to_get)
extra_CCNP_still = extra_CCNP[!(extra_CCNP %in% CCNP_ids_to_get)]
saveRDS(CCNP_files_to_get, "/media/disk2/RBC_version0.1/CCNP_files_to_get.rds")

```

```{r}
# getting missing FC files
# BHRC

subjects = paste0("sub-", c(20982))

# Base path to the datalad dataset
base_path <- paste0(RBC_path, "BHRC_CPAC/cpac_RBCv0")

# Run datalad get for each subject
for (subj in subjects) {
  run = 1
  status = 1
  while(status != 0 & run < 5){
    file_suffix = paste0("sub-11111_ses-1_task-rest_run-", run, "_acq-VARIANTNumVolumes_atlas-Schaefer2018p300n17_space-MNI152NLin6ASym_reg-36Parameter_desc-PearsonNilearn_correlations.tsv")
    subj_file <- file.path(base_path, subj, "ses-1/func", gsub("sub-[^_]+", subj, file_suffix))
  cat("Getting", subj_file, "\n")
    status <- system2("datalad", c("get", subj_file))
  
  if (status != 0) {
    message("Error getting file: ", subj_file)
    # increase run
    run = run + 1
  } else {
    message("Successfully got: ", subj_file)
  }
  }
}

```

# Assembling FC data

```{r}
FC_pattern = ".*_task-rest.*atlas-Schaefer2018p300n17_.*36Parameter_desc-PearsonNilearn_correlations.tsv$"
for (s in studies){
  # Define the directory containing the subject folders
  base_dir <- paste0("/media/disk2/RBC_version0.1/", s, "_CPAC/cpac_RBCv0")

  # Find all the FC files recursively
  assign(paste0("FC_files_",s), list.files(
    path = base_dir,
    pattern = FC_pattern,
    full.names = TRUE,
    recursive = TRUE
  ))

  assign(paste0("downloaded_FC_ids_", s), gsub(".*(sub-[^_/]+).*", "\\1", get(paste0("FC_files_", s))))
}
```


```{r}
# the ones still "missing" should  be structural artifact (not full pass)
# check against QC
func_qc_keep_BHRC <- func_qc_BHRC %>% filter(session_id == 1 & fmriExclude == 0 & task == "rest")
length(unique(func_qc_keep_BHRC$participant_id))
length(unique(downloaded_FC_ids_BHRC))
which(!(unique(func_qc_keep_BHRC$participant_id) %in% as.numeric(gsub("sub-", "", unique(downloaded_FC_ids_BHRC)))))

func_qc_keep_CCNP <- func_qc_CCNP %>% filter(session_id == 1 & fmriExclude == 0 & task == "rest")
length(unique(func_qc_keep_CCNP$participant_id))
length(unique(downloaded_FC_ids_CCNP))
unique(func_qc_keep_CCNP$participant_id)[which(!(unique(func_qc_keep_CCNP$participant_id) %in%  gsub("sub-", "", unique(downloaded_FC_ids_CCNP))))]

func_qc_keep_HBN <- func_qc_HBN %>% filter(fmriExclude == 0 & task == "rest")
length(unique(func_qc_keep_HBN$participant_id))
length(unique(downloaded_FC_ids_HBN))
which(!(unique(func_qc_keep_HBN$participant_id) %in% gsub("sub-", "", unique(downloaded_FC_ids_HBN))))

func_qc_keep_NKI <- func_qc_NKI %>% filter(session_id %in% c("BAS1", "BAS2") & fmriExclude == 0 & task == "rest")
length(unique(func_qc_keep_NKI$participant_id))
length(unique(downloaded_FC_ids_NKI))
which(!(unique(func_qc_keep_NKI$participant_id) %in% gsub("sub-", "", unique(downloaded_FC_ids_NKI))))

func_qc_keep_PNC <- func_qc_PNC %>% filter(fmriExclude == 0 & task == "rest")
length(unique(func_qc_keep_PNC$participant_id))
length(unique(downloaded_FC_ids_PNC))
which(!(unique(func_qc_keep_PNC$participant_id) %in%  gsub("sub-", "", unique(downloaded_FC_ids_PNC))))



# compare to structural ids
struct_all = read.csv(paste0(RBC_path, "regional_GMV_all_sites_unharmonized.csv"))
struct_ids_BHRC = unlist(struct_all %>% filter(study == "BHRC") %>% select(participant_id))
length(struct_ids_BHRC); length(unique(downloaded_FC_ids_BHRC)); length(unique(func_qc_keep_BHRC$participant_id)) # 424 vs 539 vs 461
struct_ids_BHRC[(!(struct_ids_BHRC %in% as.numeric(gsub("sub-", "", unique(downloaded_FC_ids_BHRC)))))] # these 3 extra passed structural but not functional - seems like they shouldn't have been included in complete-pass?
length(which(unique(func_qc_keep_BHRC$participant_id) %in% struct_ids_BHRC)) # 417
struct_qc_ids_BHRC = unlist(t1_qc_BHRC %>% filter(qc_determination == "Pass" & session_id==1) %>% select(participant_id))
struct_qc_ids_BHRC[which(!(struct_qc_ids_BHRC %in% struct_ids_BHRC))] # none

struct_ids_CCNP = unlist(struct_all %>% filter(study == "Colornest") %>% select(participant_id))
length(struct_ids_CCNP); length(unique(downloaded_FC_ids_CCNP)); length(unique(func_qc_keep_CCNP$participant_id)) # 178 vs 178 vs 194
struct_ids_CCNP[(!(struct_ids_CCNP %in% gsub("sub-", "", unique(downloaded_FC_ids_CCNP))))] # none
length(which(unique(func_qc_keep_CCNP$participant_id) %in% struct_ids_CCNP)) # all
struct_qc_ids_CCNP = unlist(t1_qc_CCNP %>% filter(qc_determination == "Pass" &session_id==1) %>% select(participant_id))
struct_qc_ids_CCNP[which(!(struct_qc_ids_CCNP %in% struct_ids_CCNP))] # none

struct_ids_HBN = unlist(struct_all %>% filter(study == "HBN") %>% select(participant_id))
length(struct_ids_HBN); length(unique(downloaded_FC_ids_HBN)); length(unique(func_qc_keep_HBN$participant_id)) # 1390 vs 1286 vs 1891
struct_ids_HBN[(!(struct_ids_HBN %in% gsub("sub-", "", unique(downloaded_FC_ids_HBN))))] # many extra, quick spot check shows could be for other tasks
length(which(unique(func_qc_keep_HBN$participant_id) %in% struct_ids_HBN)) # 1189
struct_qc_ids_HBN = unlist(t1_qc_HBN %>% filter(qc_determination == "Pass") %>% select(participant_id))
which(!(unique(func_qc_keep_HBN$participant_id) %in% gsub("sub-", "", unique(downloaded_FC_ids_HBN))) & unique(func_qc_keep_HBN$participant_id) %in% struct_qc_ids_HBN) #none
struct_qc_ids_HBN[which(!(struct_qc_ids_HBN %in% struct_ids_HBN))] # none


struct_ids_NKI = unlist(struct_all %>% filter(study == "NKI") %>% select(participant_id))
length(struct_ids_NKI); length(unique(downloaded_FC_ids_NKI)); length(unique(func_qc_keep_NKI$participant_id)) # 1075 vs 1161 vs 1254
struct_ids_NKI[(!(struct_ids_NKI %in% gsub("sub-", "", unique(downloaded_FC_ids_NKI))) & struct_ids_NKI %in% func_qc_keep_NKI$participant_id)] # none 
length(which(unique(func_qc_keep_NKI$participant_id) %in% struct_ids_NKI)) # 1059
struct_qc_ids_NKI = unlist(t1_qc_NKI %>% filter(qc_determination == "Pass" &session_id==1) %>% select(participant_id))
struct_qc_ids_NKI[which(!(struct_qc_ids_NKI %in% struct_ids_NKI))] # none


struct_ids_PNC = unlist(struct_all %>% filter(study == "PNC") %>% select(participant_id))
length(struct_ids_PNC); length(unique(downloaded_FC_ids_PNC)); length(unique(func_qc_keep_PNC$participant_id)) # 1439 vs 1227 vs 1321
struct_ids_PNC[(!(struct_ids_PNC %in% gsub("sub-", "", unique(downloaded_FC_ids_PNC))) & struct_ids_PNC %in% func_qc_keep_PNC$participant_id)] # none
length(which(unique(func_qc_keep_PNC$participant_id) %in% struct_ids_PNC)) # 1227
struct_qc_ids_PNC = unlist(t1_qc_PNC %>% filter(qc_determination == "Pass" &session_id==1) %>% select(participant_id))
struct_qc_ids_PNC[which(!(struct_qc_ids_PNC %in% struct_ids_PNC))] # none


```

```{r}
all_FC_files = c(FC_files_BHRC, FC_files_CCNP, FC_files_HBN, FC_files_NKI, FC_files_PNC)
# remove duplicated subject files (should be between 4070 based on overlap of functional QC and structural IDs and 5118 based on functional QC)
all_func_qc_keep_ids = c(unique(func_qc_keep_BHRC$participant_id), unique(func_qc_keep_CCNP$participant_id), unique(func_qc_keep_HBN$participant_id), unique(func_qc_keep_NKI$participant_id), unique(func_qc_keep_PNC$participant_id))
all_func_struct_overlap_ids = all_func_qc_keep_ids[which(all_func_qc_keep_ids %in% sub(".*sub-([^_/]+).*", "\\1",c(all_struct_ids_BHRC, all_struct_ids_CCNP, all_struct_ids_HBN, all_struct_ids_NKI, all_struct_ids_PNC)))]

all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)

# all_FC_downloaded_ids[which(!(all_FC_downloaded_ids %in% all_func_qc_keep_ids))] # all BHRC extra downloaded files are either excluded by QC or not baseline session, HBN excluded by QC, NKI either excluded by QC, not baseline, or not rest. Can safely remove these subjects from the file vector to load in

all_FC_files = all_FC_files[-which(!(all_FC_downloaded_ids %in% all_func_qc_keep_ids))]
all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)
length(unique(all_FC_downloaded_ids))


all_FC_downloaded_ids[which(!(all_FC_downloaded_ids %in% all_func_struct_overlap_ids))] 

# remove any session 2
all_FC_files = all_FC_files[-c(grep("ses-2", all_FC_files))]
all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)

duplicated_ids = all_FC_downloaded_ids[which(duplicated(all_FC_downloaded_ids))]
grep(duplicated_ids[1], all_FC_files, value = T)

# remove higher runs when lower run available
deduplicate_fc_by_run <- function(fc_files) {
  #browser()
  # Track original index
  original_index <- seq_along(fc_files)

  # Extract subject IDs and run numbers
  subj_ids <- sub(".*(sub-[^/]+)/.*", "\\1", fc_files)
  run_nums <- as.integer(sub(".*run-([0-9]+).*", "\\1", fc_files)) # NA for those with no run information - keep for now

  # Combine into a data.frame
  df <- data.frame(file = fc_files, subject = subj_ids, run = run_nums, index = original_index, stringsAsFactors = FALSE)
  # Split into two groups
  with_run <- df[!is.na(df$run), ]
  no_run <- df[is.na(df$run), ]

  # For files with run numbers, keep lowest run per subject
  keep_with_run <- with_run[ave(with_run$run, with_run$subject, FUN = min) == with_run$run, ]
  
   # Combine and re-sort by original order
  final_df <- rbind(keep_with_run, no_run)
  final_df <- final_df[order(final_df$index), ]

  return(final_df$file)
}

all_FC_files_copy = all_FC_files
all_FC_files = deduplicate_fc_by_run(all_FC_files)

```

```{r}
all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)

duplicated_ids = all_FC_downloaded_ids[which(duplicated(all_FC_downloaded_ids))] # all from NKI or PNC
grep(duplicated_ids[1], all_FC_files, value = T)

# NKI has 3 acquisition protocols: singlebad (CAP) for reference, multiband 645 and multiband 1400
func_qc_keep_NKI %>% group_by(acq) %>% summarize(mean(medianFD))
# 645 is best temporal resolution and lowest avg median FD
deduplicate_fc_NKI_files <- function(fc_files) {
  #browser()
  # Track original index
  original_index <- seq_along(fc_files)

  # Extract subject IDs, study, acq
  subj_ids <- sub(".*(sub-[^/]+)/.*", "\\1", fc_files)
  study_ids <- sub(".*/RBC_version0.1/([A-Z]+)_.*", "\\1", fc_files)
  acq <- sub(".*acq-([A-Za-z0-9]+)_.*", "\\1", fc_files)
  session_ids <-  sub(".*ses-([A-Za-z0-9]+)_.*", "\\1", fc_files)
  

  # Combine into a data.frame
  df <- data.frame(file = fc_files, subject = subj_ids, study = study_ids, session = session_ids, acq = acq, index = original_index, stringsAsFactors = FALSE)
  
  # Split into NKI vs other
  NKI <- df[df$study == "NKI", ]
  other <- df[df$study != "NKI", ]

  # For NKI, get file with most preferred acquisition (645 > 1400 > 2500) and session (BAS1 > BAS2)
  keep_NKI <- NKI %>%
    filter(session %in% c("BAS1", "BAS2")) %>%
  mutate(
    priority = case_when(
      grepl("645", file) ~ 1,
      grepl("1400", file) ~ 2,
      grepl("CAP", file) ~ 3,
      TRUE ~ 99  # lowest priority for anything else
    )
  ) %>%
  group_by(subject) %>%
  arrange(session, priority, .by_group = TRUE) %>% # keep earliest session with most preferred acq
  slice(1) %>%
  ungroup() %>%
  select(-priority)
  
   # Combine and re-sort by original order
  final_df <- rbind(keep_NKI, other)
  final_df <- final_df[order(final_df$index), ]

  return(final_df$file)
}

all_FC_files = deduplicate_fc_NKI_files(all_FC_files)
```

```{r}
all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)
duplicated_ids = all_FC_downloaded_ids[which(duplicated(all_FC_downloaded_ids))] # all fromPNC
grep(duplicated_ids[1], all_FC_files, value = T) # different acq - can't find documentation for "100"

deduplicate_fc_PNC_files <- function(fc_files) {
  #browser()
  # Track original index
  original_index <- seq_along(fc_files)

  # Extract subject IDs, study, acq
  subj_ids <- sub(".*(sub-[^/]+)/.*", "\\1", fc_files)
  study_ids <- sub(".*/RBC_version0.1/([A-Z]+)_.*", "\\1", fc_files)
  acq <- sub(".*acq-([A-Za-z0-9]+)_.*", "\\1", fc_files)

  # Combine into a data.frame
  df <- data.frame(file = fc_files, subject = subj_ids, study = study_ids, acq = acq, index = original_index, stringsAsFactors = FALSE)
  
  # Split into PNC vs other
  PNC <- df[df$study == "PNC", ]
  other <- df[df$study != "PNC", ]

  # For PNC, get file with most preferred acquisition (singleband > 100)
  keep_PNC <- PNC %>%
  mutate(
    priority = case_when(
      grepl("singleband", file) ~ 1,
      grepl("100", file) ~ 2,
      TRUE ~ 99  # lowest priority for anything else
    )
  ) %>%
  group_by(subject) %>%
  arrange(priority, .by_group = TRUE) %>% 
  slice(1) %>%
  ungroup() %>%
  select(-priority)
  
   # Combine and re-sort by original order
  final_df <- rbind(keep_PNC, other)
  final_df <- final_df[order(final_df$index), ]

  return(final_df$file)
}

all_FC_files = deduplicate_fc_PNC_files(all_FC_files)

all_FC_downloaded_ids = sub(".*sub-([^_/]+).*", "\\1", all_FC_files)
duplicated_ids = all_FC_downloaded_ids[which(duplicated(all_FC_downloaded_ids))] # no more duplicates!
length(all_FC_downloaded_ids) #4173 total

all_FC_files_to_get <- all_FC_files[!file.exists(all_FC_files)]
saveRDS(all_FC_files_to_get, "/media/disk2/RBC_version0.1/files_to_get.rds")
```

```{r}
# combine all demo and qc data across studies
demo_all = rbind(demo_BHRC, demo_CCNP, demo_HBN, demo_NKI, demo_PNC)
func_qc_keep_all = rbind(func_qc_keep_BHRC, func_qc_keep_CCNP, func_qc_keep_HBN, func_qc_keep_NKI, func_qc_keep_PNC)

# regional labels
schaefer_atlas = read_tsv("/media/disk2/RBC_version0.1/atlas-Schaefer2018_space-MNI152NLin6_res-2_desc-300Parcels17NetworksOrder_dseg.tsv")
# remove background region
schaefer_atlas %<>% filter(index!=0)
region_labels = gsub("17Networks_", "", schaefer_atlas$label)
network17_id = sub("^[^_]+_([^_]+)_.*$", "\\1", region_labels)
# get 7 network ids
# Create a lookup table for 17-to-7 network mapping
yeo17_to_7 <- c("VisCent" = "Visual", "VisPeri" = "Visual",
                "SomMotA" = "Somatomotor", "SomMotB" = "Somatomotor",
                "DorsAttnA" = "DorsalAttn", "DorsAttnB" = "DorsalAttn",
                "SalVentAttnA" = "VentralAttn", "SalVentAttnB" = "VentralAttn",
                "LimbicA" = "Limbic", "LimbicB" = "Limbic",
                "ContA" = "Control", "ContB" = "Control", "ContC" = "Control",
                "DefaultA" = "Default", "DefaultB" = "Default", "DefaultC" = "Default", "TempPar" = "Default")

# Map to 7-network labels
network7_id <- yeo17_to_7[network17_id]

region_connection_names = matrix(NA, nrow = 300, ncol = 300)
for (i in 1:nrow(region_connection_names)){
  region_connection_names[i, ] =  paste0(region_labels[i], "_to_", region_labels)
}
region_connection_names = region_connection_names[lower.tri(region_connection_names)]

network17_connection_names = matrix(NA, nrow =300, ncol =300)
for (i in 1:nrow(network17_connection_names)){
  network17_connection_names[i, ] =  paste0(network17_id[i], "_to_", network17_id)
}
network17_connection_names = network17_connection_names[lower.tri(network17_connection_names)]
# organize the regions connection names
network17_connection_names_clean = lapply(network17_connection_names, function(x) {
  strsplit(x, "_to_") %>% unlist %>% sort %>% paste0(collapse = "_to_")
}) %>% unlist

network7_connection_names = matrix(NA, nrow = 300, ncol = 300)
for (i in 1:nrow(network7_connection_names)){
  network7_connection_names[i, ] =  paste0(network7_id[i], "_to_", network7_id)
}
network7_connection_names = network7_connection_names[lower.tri(network7_connection_names)]
# organize the regions connection names
network7_connection_names_clean = lapply(network7_connection_names, function(x) {
  strsplit(x, "_to_") %>% unlist %>% sort %>% paste0(collapse = "_to_")
}) %>% unlist

library(pbapply)

FC_data <- pblapply(all_FC_files, function(f){
  #browser()
  # read in file
  FC <- read_tsv(f, col_names = F, show_col_types = FALSE)
  
  # vector of regional connections
  FC_regional <- FC[lower.tri(FC)]
  names(FC_regional) <- region_connection_names
  
  # 7 network means
  temp = data.frame(FC = network7_connection_names_clean, Z = FC_regional)
  temp = temp %>% group_by(FC) %>% summarise(mean_Z = mean(Z))
  
  FC_7_network = temp$mean_Z
  names(FC_7_network) = temp$FC
  
  # 17 network means
  temp = data.frame(FC = network17_connection_names_clean, Z = FC_regional)
  temp = temp %>% group_by(FC) %>% summarise(mean_Z = mean(Z))
  
  FC_17_network = temp$mean_Z
  names(FC_17_network) = temp$FC
  
  # add in subject id demographic
  subj = sub(".*sub-([^_/]+).*", "\\1", f)
  # session id to match demographic
  session_id <-  sub(".*ses-([A-Za-z0-9]+)_.*", "\\1", f)
  demo_sub = demo_all[as.character(demo_all$participant_id) == subj & demo_all$session_id == session_id,]
  # add in QC
  acq <- sub(".*acq-([A-Za-z0-9]+)_.*", "\\1", f)
  run <- sub(".*run-([0-9]+)_.*", "\\1", f)
  qc_sub = func_qc_keep_all[as.character(func_qc_keep_all$participant_id) == subj & func_qc_keep_all$session_id == session_id & (func_qc_keep_all$acq == acq | is.na(func_qc_keep_all$acq)) & (func_qc_keep_all$run == run | is.na(func_qc_keep_all$run)),]
  
  if(nrow(qc_sub) > 1){
    warning(paste0("Check ID = ", subj))
  }
  
  FC_regional = cbind(demo_sub, qc_sub, t(as.data.frame(FC_regional)))
  FC_7_network = cbind(demo_sub, qc_sub, t(as.data.frame(FC_7_network)))
  FC_17_network = cbind(demo_sub, qc_sub, t(as.data.frame(FC_17_network)))
  
  return(list(FC_regional = FC_regional, FC_7_network = FC_7_network, FC_17_network = FC_17_network))
})


# save very large dataset before more manipulation since above code took ~45 mins to run
saveRDS(FC_data, "/media/disk2/multivariateBWAS/RBC_sims/FC_data.rds")
```

```{r}
# combine FC rows
library(purrr)
FC_regional <- map(FC_data, 1) %>% bind_rows()
FC_network7   <- map(FC_data, 2) %>% bind_rows()
FC_network17  <- map(FC_data, 3) %>% bind_rows()

# forgot to remove the duplicate participant/session id
FC_regional %<>% select(-c(participant_id...42, session_id...44))
FC_regional %<>% rename(participant_id = "participant_id...1", session_id = "session_id...2")
FC_network7 %<>% select(-c(participant_id...42, session_id...44))
FC_network7 %<>% rename(participant_id = "participant_id...1", session_id = "session_id...2")
FC_network17 %<>% select(-c(participant_id...42, session_id...44))
FC_network17 %<>% rename(participant_id = "participant_id...1", session_id = "session_id...2")

write.csv(FC_regional, "/media/disk2/RBC_version0.1/FC_regional_unharmonized.csv")
write.csv(FC_network7, "/media/disk2/RBC_version0.1/FC_network7_unharmonized.csv")
write.csv(FC_network17, "/media/disk2/RBC_version0.1/FC_network17_unharmonized.csv")

# 4173 participants with FC
# 3161 after harmonizing with covariates
# overlap of 3074 with the 3486 structural harmonized ids
```


# CovBat

Save versions of the data that have had site effects addressed via CovBat

## Structural

```{r}
library(CovBat)
struct_all = read.csv(paste0(RBC_path, "regional_GMV_all_sites_unharmonized.csv"))


data_struct_schaefer_covbat = covbat(dat = t(struct_all[,grep("17Networks", colnames(struct_all), value = T)]),
                            bat = struct_all$study_site)

data_struct_DKT_covbat = covbat(dat = t(struct_all[,c(grep("lh_", colnames(struct_all), value = T), grep("rh_", colnames(struct_all), value = T))]),
                            bat = struct_all$study_site)

data_struct_harmonized = struct_all
data_struct_harmonized[,grep("17Networks", colnames(struct_all), value = T)] = t(data_struct_schaefer_covbat$dat.covbat)
data_struct_harmonized[,c(grep("lh_", colnames(struct_all), value = T), grep("rh_", colnames(struct_all), value = T))] = t(data_struct_DKT_covbat$dat.covbat)

# save harmonized data
write.csv(data_struct_harmonized, paste0(RBC_path,  "regional_GMV_all_sites_harmonized.csv"))


# including covariates
covariates = model.matrix(~ age + sex + p_factor_mcelroy_harmonized_all_samples + internalizing_mcelroy_harmonized_all_samples + externalizing_mcelroy_harmonized_all_samples + attention_mcelroy_harmonized_all_samples, struct_all)


struct_all_cov = na.omit(struct_all[,c("participant_id","study_site", "study", "age", "sex", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples", "p_factor_mcelroy_harmonized_all_samples", "attention_mcelroy_harmonized_all_samples", grep("17Networks", colnames(struct_all), value = T), grep("^(lh_|rh_)", colnames(struct_all), value = TRUE))])

data_struct_schaefer_covbat_cov = covbat(dat = t(struct_all_cov[,grep("17Networks", colnames(struct_all_cov), value = T)]),
                            bat = struct_all_cov$study_site, mod = covariates)

data_struct_DKT_covbat_cov = covbat(dat = t(struct_all_cov[,c(grep("lh_", colnames(struct_all_cov), value = T), grep("rh_", colnames(struct_all_cov), value = T))]),
                            bat = struct_all_cov$study_site, mod = covariates)

data_struct_harmonized_cov = struct_all_cov
data_struct_harmonized_cov[,grep("17Networks", colnames(struct_all_cov), value = T)] = t(data_struct_schaefer_covbat_cov$dat.covbat)
data_struct_harmonized_cov[,c(grep("lh_", colnames(struct_all_cov), value = T), grep("rh_", colnames(struct_all_cov), value = T))] = t(data_struct_DKT_covbat_cov$dat.covbat)

# merge back in other demographic data
new_cols <- c("participant_id", setdiff(names(struct_all), names(data_struct_harmonized_cov)))
struct_all_subset <- struct_all[, new_cols]
data_struct_harmonized_cov = merge(data_struct_harmonized_cov, struct_all_subset, by = "participant_id")

# save harmonized data
write.csv(data_struct_harmonized_cov, paste0(RBC_path,  "regional_GMV_all_sites_harmonized_covariates.csv"))




```

## Functional

```{r}
## regional
FC_regional = read.csv(paste0(RBC_path, "FC_regional_unharmonized.csv"))


FC_regional_covbat = covbat(dat = t(FC_regional[,grep("_to_", colnames(FC_regional), value = T)]),
                            bat = FC_regional$study_site)


FC_regional_harmonized = FC_regional
FC_regional_harmonized[,grep("_to_", colnames(FC_regional), value = T)] = t(FC_regional_covbat$dat.covbat)

# save harmonized data
write.csv(FC_regional_harmonized, paste0(RBC_path,  "FC_regional_harmonized.csv"))

# including covariates
covariates = model.matrix(~ age + sex + p_factor_mcelroy_harmonized_all_samples + internalizing_mcelroy_harmonized_all_samples + externalizing_mcelroy_harmonized_all_samples + attention_mcelroy_harmonized_all_samples, FC_regional)


FC_regional_cov = na.omit(FC_regional[,c("participant_id","study_site", "study", "age", "sex", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples", "p_factor_mcelroy_harmonized_all_samples", "attention_mcelroy_harmonized_all_samples", grep("_to_", colnames(FC_regional), value = T))])

FC_regional_covbat_cov = covbat(dat = t(FC_regional_cov[,grep("_to_", colnames(FC_regional_cov), value = T)]),
                            bat = FC_regional_cov$study_site, mod = covariates)

FC_regional_harmonized_cov = FC_regional_cov
FC_regional_harmonized_cov[,grep("_to_", colnames(FC_regional_cov), value = T)] = t(FC_regional_covbat_cov$dat.covbat)

# merge back in other demographic data
new_cols <- c("participant_id", setdiff(names(FC_regional), names(FC_regional_harmonized_cov)))
FC_regional_subset <- FC_regional[, new_cols]
FC_regional_harmonized_cov = merge(FC_regional_harmonized_cov, FC_regional_subset, by = "participant_id")

# save harmonized data
write.csv(FC_regional_harmonized_cov, paste0(RBC_path,  "FC_regional_harmonized_covariates.csv"))


## 7 Network
FC_network7 = read.csv(paste0(RBC_path, "FC_network7_unharmonized.csv"))


FC_network7_covbat = covbat(dat = t(FC_network7[,grep("_to_", colnames(FC_network7), value = T)]),
                            bat = FC_network7$study_site)


FC_network7_harmonized = FC_network7
FC_network7_harmonized[,grep("_to_", colnames(FC_network7), value = T)] = t(FC_network7_covbat$dat.covbat)

# save harmonized data
write.csv(FC_network7_harmonized, paste0(RBC_path,  "FC_network7_harmonized.csv"))

# including covariates
covariates = model.matrix(~ age + sex + p_factor_mcelroy_harmonized_all_samples + internalizing_mcelroy_harmonized_all_samples + externalizing_mcelroy_harmonized_all_samples + attention_mcelroy_harmonized_all_samples, FC_network7)


FC_network7_cov = na.omit(FC_network7[,c("participant_id","study_site", "study", "age", "sex", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples", "p_factor_mcelroy_harmonized_all_samples", "attention_mcelroy_harmonized_all_samples", grep("_to_", colnames(FC_network7), value = T))])

FC_network7_covbat_cov = covbat(dat = t(FC_network7_cov[,grep("_to_", colnames(FC_network7_cov), value = T)]),
                            bat = FC_network7_cov$study_site, mod = covariates)

FC_network7_harmonized_cov = FC_network7_cov
FC_network7_harmonized_cov[,grep("_to_", colnames(FC_network7_cov), value = T)] = t(FC_network7_covbat_cov$dat.covbat)

# merge back in other demographic data
new_cols <- c("participant_id", setdiff(names(FC_network7), names(FC_network7_harmonized_cov)))
FC_network7_subset <- FC_network7[, new_cols]
FC_network7_harmonized_cov = merge(FC_network7_harmonized_cov, FC_network7_subset, by = "participant_id")

# save harmonized data
write.csv(FC_network7_harmonized_cov, paste0(RBC_path,  "FC_network7_harmonized_covariates.csv"))

## 17 network
FC_network17 = read.csv(paste0(RBC_path, "FC_network17_unharmonized.csv"))


FC_network17_covbat = covbat(dat = t(FC_network17[,grep("_to_", colnames(FC_network17), value = T)]),
                            bat = FC_network17$study_site)


FC_network17_harmonized = FC_network17
FC_network17_harmonized[,grep("_to_", colnames(FC_network17), value = T)] = t(FC_network17_covbat$dat.covbat)

# save harmonized data
write.csv(FC_network17_harmonized, paste0(RBC_path,  "FC_network17_harmonized.csv"))

# including covariates
covariates = model.matrix(~ age + sex + p_factor_mcelroy_harmonized_all_samples + internalizing_mcelroy_harmonized_all_samples + externalizing_mcelroy_harmonized_all_samples + attention_mcelroy_harmonized_all_samples, FC_network17)


FC_network17_cov = na.omit(FC_network17[,c("participant_id","study_site", "study", "age", "sex", "internalizing_mcelroy_harmonized_all_samples", "externalizing_mcelroy_harmonized_all_samples", "p_factor_mcelroy_harmonized_all_samples", "attention_mcelroy_harmonized_all_samples", grep("_to_", colnames(FC_network17), value = T))])

FC_network17_covbat_cov = covbat(dat = t(FC_network17_cov[,grep("_to_", colnames(FC_network17_cov), value = T)]),
                            bat = FC_network17_cov$study_site, mod = covariates)

FC_network17_harmonized_cov = FC_network17_cov
FC_network17_harmonized_cov[,grep("_to_", colnames(FC_network17_cov), value = T)] = t(FC_network17_covbat_cov$dat.covbat)

# merge back in other demographic data
new_cols <- c("participant_id", setdiff(names(FC_network17), names(FC_network17_harmonized_cov)))
FC_network17_subset <- FC_network17[, new_cols]
FC_network17_harmonized_cov = merge(FC_network17_harmonized_cov, FC_network17_subset, by = "participant_id")

# save harmonized data
write.csv(FC_network17_harmonized_cov, paste0(RBC_path,  "FC_network17_harmonized_covariates.csv"))



```